---
title: "HDD Data Download from SQL Server"
author: "Yao"
date: "May 23, 2018"
output: html_document
---

Updated on 07/18/2018.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(feather)
options(scipen = 999)
```

## Load Database from SQL Server

```{r ConnectDB}
library(DBI)
db = dbConnect(odbc::odbc(),
               driver = 'SQL Server',
               server = 'IRISAGL01.aus.amer.dell.com',
               user = 'Yao_Z',
               password = 'y67uhgt$Y')
```

It is not well known that you can run SQL code in an R Notebook code chunk. To use SQL, open an R Notebook in the RStudio IDE under the File > New File menu. Start a new code chunk with {sql}, and specify your connection with the connection=con code chunk option. If you want to send the query output to an R dataframe use output.var = "mydataframe" in the code chunk options. When you specify output.var you will be able to use the output in subsequent R code chunks. In this example, we use the output in ggplot.

```{sql hdd_qty, connection=db, output.var = 'hdd_qty'}
SELECT 
  D.Cfg_Desc AS CFG, D.sku_num, D.Sample_DPN, C.Fiscal_Qtr, C.Fiscal_Mo, C.Fiscal_Wk, C.Fiscal_Wk_End_Date, C.Fiscal_Date, C.Fiscal_Yr, B.Order_Date_week, C.Fiscal_Mo_End_Date,  C.Fiscal_Qtr_End_Date,
  CASE WHEN A.LOB_DESC = 'PowerEdge' AND A.ESI_order_flag = 'Y' THEN 'PowerEdge - ESI'
                     WHEN A.MGMT_PROD_LVL_3_NM = 'Storage' AND A.DELL_EMC_ORDER_FLAG = 'DELL' THEN 'Storage - DELL'
                ELSE A.LOB_DESC END AS LOB_DESC, A.BRAND_CATG_DESC, 
  A.RGN_DESC,
  A.GBL_PARNT_ACCT_NM AS Customer, 
  SUM(SYS_QTY_DELL) AS SYS_QTY,
  SUM(ITM_QTY) AS PART_QTY
FROM IRIS.[Base].[ISG_Business_Transformation.isgOrders] AS A 
JOIN IRIS.[Base].[ISG_Business_Transformation.isgOrdersDetails] B
ON A.ORD_NBR = B.ORD_NBR AND A.FMLY_PFOLIO_DESC = B.FMLY_PFOLIO_DESC AND A.SRC_BU_ID = B.SRC_BU_ID
JOIN IRIS.DIM.Date C
ON B.ORD_DT = C.Fiscal_Date
JOIN IRIS_Data_Mart.[dbo].[SKU_CFG_Bridge] D
ON B.ITM_NBR = D.sku_num
WHERE D.Cfg_Desc LIKE '%HDD%' AND Commodity_Desc IN ('Hard Drive', 'Controller Cards/HBA') AND A.DELL_EMC_ORDER_FLAG = 'DELL' AND (A.LOB_DESC IN ('PowerEdge','Cloud Products') OR A.MGMT_PROD_LVL_3_NM = 'Storage') ---AND C.Fiscal_Yr >= 'FY16'
GROUP BY
  D.Cfg_Desc, D.sku_num, D.Sample_DPN, C.Fiscal_Qtr, C.Fiscal_Mo, C.Fiscal_Wk, C.Fiscal_Wk_End_Date, C.Fiscal_Date, C.Fiscal_Yr, B.Order_Date_week, C.Fiscal_Mo_End_Date,  C.Fiscal_Qtr_End_Date,
  CASE WHEN A.LOB_DESC = 'PowerEdge' AND A.ESI_order_flag = 'Y' THEN 'PowerEdge - ESI'
                   WHEN A.MGMT_PROD_LVL_3_NM = 'Storage' AND A.DELL_EMC_ORDER_FLAG = 'DELL' THEN 'Storage - DELL'
                   ELSE A.LOB_DESC END, A.BRAND_CATG_DESC, 
  A.RGN_DESC, A.GBL_PARNT_ACCT_NM
ORDER BY D.Cfg_Desc, C.Fiscal_Qtr, C.Fiscal_Mo, C.Fiscal_Wk
```


```{r Deal with missing data}
Weekly_HDD_QTY_combined <- hdd_qty %>% group_by(Order_Date_week,Fiscal_Wk) %>% summarise(Fiscal_Wk_QTY=sum(PART_QTY))

apply(hdd_qty, 2, function(x) any(is.na(x)))

# Columns have NA: Customer
hdd_qty = hdd_qty %>% 
  mutate(Customer = ifelse(
    grepl('Dummy|disti|\032|APPOINTED|ACCT-R', Customer, ignore.case = T) | Customer == '' | is.na(Customer),
    'Unknown_Customer', Customer
  ))

apply(hdd_qty, 2, function(x) any(is.na(x)))
# All NAs have been cleaned.

write_feather(hdd_qty,'~/Yao_Rdata/HDD_QTY_IRIS.feather')
```


```{sql connection=db, output.var = 'mrp_data0'}
SELECT [VERSION], MONWKYR, CFG, REGION, SUM(DATA) AS MRP_CT, Commodity_Desc
FROM IRIS.Base.MRP_Weekly A
JOIN IRIS.DIM.DPN B 
ON A.PART = B.DPN
WHERE B.CFG LIKE '%HDD%' AND B.Commodity_Desc IN ('Hard Drive')--Verified with other restrictions. Good for now.
GROUP BY [VERSION], MONWKYR, CFG, REGION, Commodity_Desc
```

```{r}
write_feather(mrp_data0,'~/Yao_Rdata/mrp_HDD.feather')

mrp_data <- mrp_data0
# Extract Month,Week,Year from MONWKYR
mrp_data$MON <- substr(mrp_data$MONWKYR, start = 1, stop = 3)
mrp_data$WK <- substr(mrp_data$MONWKYR, start = 5, stop = 5)
mrp_data$YR <- substr(mrp_data$MONWKYR, start = 6, stop = 7)
mrp_data$YRMON <- paste(mrp_data$YR,mrp_data$MON)

#mrp_data[c("MON","WK","YR")] <- lapply(mrp_data[c("MON","WK","YR")], function(x) as.factor(as.character(x)))

mrp_data %>% 
  mutate(VERSION = factor(VERSION, levels = c("FY19Q2W5","FY19Q2W6","FY19Q2W7","FY19Q2W8","FY19Q2W9","FY19Q2W10"))) %>%
  #mutate(MON = factor(MON, levels = c('JUN','JUL','AUG','SEP','OCT','NOV','DEC','JAN','FEB','MAR','APR','MAY'))) %>%
  mutate(YRMON = factor(YRMON, levels = c('19 JUN','19 JUL','19 AUG','19 SEP','19 OCT','19 NOV','19 DEC','19 JAN','20 FEB','20 MAR','20 APR','20 MAY','20 JUN'))) %>%
  arrange(VERSION,CFG,REGION,YRMON,WK) -> mrp_data.ordered
```

```{sql connection=db, output.var = 'calr2Fisc_match'}
SELECT [CLDR_YYYYMMDD_VAL]
      ,[CLDR_WEEK_VAL]
      ,[CLDR_MTH_VAL]
      ,[CLDR_QTR_VAL]
      ,[FISC_WEEK_VAL]
      ,[FISC_WEEK_END_DATE]
      ,[FISC_MTH_VAL]
      ,[FISC_QTR_VAL]
      ,[FISC_YR_VAL]
	  ,[CLDR_MTH_WEEK_NUM]
  FROM [IRIS].[Base].[COMN_BASE.CORP_CLDR]
  WHERE FISC_YR_NUM>=2019 AND FISC_YR_NUM<=2020
```

```{r}
write_feather(calr2Fisc_match,'~/Yao_Rdata/calr2Fisc_match.feather')

# Preprocessing to match calender to fiscal year
calr2Fisc_match$CLDR_YR <- substr(calr2Fisc_match$CLDR_QTR_VAL,start = 1,stop = 4) # Use the CLDR Year to merge
# weekNames <- c(sprintf("FY19W0%d", 1:9),sprintf("FY19W%d", 10:52))
# cbind(1:nrow(mrp_data.ordered),weekNames) %>% data.frame() -> Fiscal_wk # This does not work since some do not have 52 weeks.
mrp_data.ordered$CLDR_YR <- case_when(mrp_data.ordered$YRMON %in% c('19 JUN','19 JUL','19 AUG','19 SEP','19 OCT','19 NOV','19 DEC')~'2019',
                                      mrp_data.ordered$YRMON %in% c('19 JAN','20 FEB','20 MAR','20 APR','20 MAY','20 JUN')~'2020')

mrp_data.ordered$WK <- as.numeric(mrp_data.ordered$WK)

mrp_data.ordered %>% left_join(select(calr2Fisc_match,CLDR_YR,CLDR_MTH_VAL,CLDR_MTH_WEEK_NUM,FISC_YR_VAL,FISC_QTR_VAL,FISC_MTH_VAL,FISC_WEEK_VAL),by = c('CLDR_YR','MON'='CLDR_MTH_VAL','WK'='CLDR_MTH_WEEK_NUM')) %>% unique() -> mrp_data.wFiscal # FISC_WEEK_END_DATE,
```


