---
title: "HDD Data Exploratory Analytics from SQL Server"
author: "Yao"
date: "May 23, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(plotly)
```

## Load Database from SQL Server

```{r ConnectDB}
library(DBI)
db = dbConnect(odbc::odbc(),
               driver = 'SQL Server',
               server = 'IRISAGL01.aus.amer.dell.com',
               user = 'Yao_Z',
               password = 'y67uhgt@Y')
```

It is not well known that you can run SQL code in an R Notebook code chunk. To use SQL, open an R Notebook in the RStudio IDE under the File > New File menu. Start a new code chunk with {sql}, and specify your connection with the connection=con code chunk option. If you want to send the query output to an R dataframe use output.var = "mydataframe" in the code chunk options. When you specify output.var you will be able to use the output in subsequent R code chunks. In this example, we use the output in ggplot.

```{sql connection=db, output.var="Weekly_HDD_QTY_OnlyDetails"}
SELECT Order_Date_week, SUM(ITM_QTY) AS HDD_QTY
FROM IRIS.[Base].[ISG_Business_Transformation.isgOrdersDetails]
WHERE ITM_TYPE = 'HDD' OR ITM_TYPE LIKE 'HARD%DRIVE%' AND DELL_EMC_ORDER_FLAG = 'DELL' AND (LOB_DESC IN ('PowerEdge','Cloud Products') OR MGMT_PROD_LVL_3_NM = 'Storage')
GROUP BY Order_Date_week
ORDER BY Order_Date_week
```


```{r plot}
Weekly_HDD_QTY_OnlyDetails %>% 
  ggplot(aes(x=Order_Date_week,y=HDD_QTY,group=1)) + 
  geom_point() +
  geom_line() +
  ggtitle('201701-201915') +
  theme(axis.text.x=element_blank(),legend.position="none")
```