---
title: "IRIS HDD Data Exploratory Analytics: CFG Clusters"
author: "Yao"
date: "June 20, 2018"
output: html_document
---

Latest update: 7/11/2018

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,fig.align="center", fig.width=10)
library(tidyverse)
library(scales)
library(ggthemes)
library(plotly)
library(reshape2)
library(imputeTS)
library(feather)
options(scipen = 999)
```


I think it is more meaningful to visualize the trends instead of the toal quantity.

```{r load the IRIS HDD Sales Data}
hdd_qty <- read_feather("~/Yao_Rdata/HDD_QTY_IRIS.feather")

# join the CFG attribute table
# CFG information
CFG.info <- read.csv("~/Yao_Excels/CFGnamesInfo_filled.csv")
hdd_qty %>% left_join(CFG.info) -> data.joined
```


```{r By Region}
# Extract Quarterly Sales for each CFG
data.joined %>% 
  group_by(CFG,Fiscal_Qtr,RGN_DESC) %>%
  summarise(HDD_QTY=sum(PART_QTY)) -> temp_qtr

p <- temp_qtr %>% ggplot(aes(x=Fiscal_Qtr,y=HDD_QTY,group = CFG, color = RGN_DESC)) +
  geom_point(size = 2) +
  geom_line(size = 1.5,alpha=0.6) +
  labs(title = 'HDD Quarterly Sales by Region', x = "Fiscal Quarter", y = "Part Quantity") +
  theme_minimal(base_size = 14) +
  scale_color_tableau('tableau10medium') +
  scale_x_discrete(breaks = c('FY17Q1', 'FY18Q1', 'FY19Q1')) +
  scale_y_continuous(label=comma) + expand_limits(y = 0) +
  facet_wrap(~RGN_DESC,ncol = 2, scales = "fixed")
ggplotly(p)
```


```{r By LOB_DESC}
#length(unique(data.joined$LOB_DESC))
# Extract Quarterly Sales for each CFG
data.joined %>% 
  group_by(CFG,Fiscal_Qtr,LOB_DESC) %>%
  summarise(HDD_QTY=sum(PART_QTY)) -> temp_qtr

p <- temp_qtr %>% ggplot(aes(x=Fiscal_Qtr,y=HDD_QTY,group = CFG, color = LOB_DESC)) +
  geom_point(size = 2) +
  geom_line(size = 1.5,alpha=0.6) +
  labs(title = 'HDD Quarterly Sales by LOB', x = "Fiscal Quarter", y = "Part Quantity") +
  theme_minimal(base_size = 14) +
  scale_color_tableau('tableau10medium') +
  scale_x_discrete(breaks = c('FY17Q1', 'FY18Q1', 'FY19Q1')) +
  scale_y_continuous(label=comma) + expand_limits(y = 0) +
  facet_wrap(~LOB_DESC,ncol = 2, scales = "fixed")
ggplotly(p)
```

```{r By Top Custermer, fig.height=20}
#length(unique(data.joined$Customer))

# Select the Top
# Only by Customer
data.joined %>% group_by(Customer) %>%
  summarise(Customer_QTY=sum(PART_QTY)) %>%
  arrange(desc(Customer_QTY))->temp_data

temp_sum <- sum(temp_data$Customer_QTY)
temp_data$Customer_Perecent <- temp_data$Customer_QTY/temp_sum*100

temp_data[1:12,] -> temp_data
print(paste('The top 12 customers occupy',round(sum(temp_data$Customer_Perecent),2),'% of the total HDD_QTY, while the top 12 customers out of',length(unique(data.joined$Customer)),'customers is',round(12/length(unique(data.joined$Customer))*100,2),'%.'))
Customer.selected <- temp_data$Customer
# The top 30 customers bought 23.00% of the HDD from FY17Q1-FY19Q2.
# Ignore the unknown customers.

# Extract Quarterly Sales for each CFG
data.joined %>% filter(Customer %in% Customer.selected) %>%
  group_by(CFG,Fiscal_Qtr,Customer) %>%
  summarise(HDD_QTY=sum(PART_QTY)) -> temp_qtr

p <- temp_qtr %>% ggplot(aes(x=Fiscal_Qtr,y=HDD_QTY,group = CFG, color = Customer)) +
  geom_point(size = 2) +
  geom_line(size = 1.5,alpha=0.6) +
  labs(title = 'HDD Quarterly Sales by Customer', x = "Fiscal Quarter", y = "Part Quantity") +
  theme_minimal(base_size = 14) +
  #scale_color_tableau('tableau10medium') +
  scale_x_discrete(breaks = c('FY17Q1', 'FY18Q1', 'FY19Q1')) +
  scale_y_continuous(label=comma) + expand_limits(y = 0) +
  facet_wrap(~Customer,ncol = 3, scales = "fixed")
ggplotly(p)
```

http://localhost:27102/session/viewhtml1d246f91061/index.html

Customer ggploty picture saved in the above link

```{r By Interface}
#length(unique(CFG.info$Interface))

# Extract Quarterly Sales for each CFG
data.joined %>% 
  group_by(CFG,Fiscal_Qtr,Interface) %>%
  summarise(HDD_QTY=sum(PART_QTY)) -> temp_qtr

p <- temp_qtr %>% ggplot(aes(x=Fiscal_Qtr,y=HDD_QTY,group = CFG, color = Interface)) +
  geom_point(size = 2) +
  geom_line(size = 1.5,alpha=0.6) +
  labs(title = 'HDD Quarterly Sales by Interface', x = "Fiscal Quarter", y = "Part Quantity") +
  theme_minimal(base_size = 14) +
  scale_color_tableau('tableau10medium') +
  scale_x_discrete(breaks = c('FY17Q1', 'FY18Q1', 'FY19Q1')) +
  scale_y_continuous(label=comma) + expand_limits(y = 0) +
  facet_wrap(~Interface,ncol = 2, scales = "fixed")
ggplotly(p)
```
SATA quantity is almost all below 100,000.
SAS shows some relatively higher and more changeable CFGs.

```{r By Interface_Speed}
#length(unique(CFG.info$Interface_Speed))

# Extract Quarterly Sales for each CFG
data.joined %>% 
  group_by(CFG,Fiscal_Qtr,Interface_Speed) %>%
  summarise(HDD_QTY=sum(PART_QTY)) -> temp_qtr

p <- temp_qtr %>% ggplot(aes(x=Fiscal_Qtr,y=HDD_QTY,group = CFG, color = Interface_Speed)) +
  geom_point(size = 2) +
  geom_line(size = 1.5,alpha=0.6) +
  labs(title = 'HDD Quarterly Sales by Interface Speed', x = "Fiscal Quarter", y = "Part Quantity") +
  theme_minimal(base_size = 14) +
  scale_color_tableau('tableau10medium') +
  scale_x_discrete(breaks = c('FY17Q1', 'FY18Q1', 'FY19Q1')) +
  scale_y_continuous(label=comma) + expand_limits(y = 0) +
  facet_wrap(~Interface_Speed,ncol = 2, scales = "fixed")
ggplotly(p)
```
Only two CFGs belong to 3G.
6G CFGs seem stable.
12G has some higher quantity.

```{r By Capacity}
#length(unique(CFG.info$Capacity))
# Need to be delt with first

# Extract Quarterly Sales for each CFG
data.joined %>% 
  group_by(CFG,Fiscal_Qtr,Capacity) %>%
  summarise(HDD_QTY=sum(PART_QTY)) -> temp_qtr

temp_qtr$Capacity <- as.factor(temp_qtr$Capacity)

p <- temp_qtr %>% ggplot(aes(x=Fiscal_Qtr,y=HDD_QTY,group = CFG, color = Capacity)) +
  geom_point(size = 2) +
  geom_line(size = 1.5,alpha=0.6) +
  labs(title = 'HDD Quarterly Sales by Capacity', x = "Fiscal Quarter", y = "Part Quantity") +
  theme_minimal(base_size = 14) +
  #scale_color_tableau('tableau10medium') +
  scale_x_discrete(breaks = c('FY17Q1', 'FY18Q1', 'FY19Q1')) +
  scale_y_continuous(label=comma) + expand_limits(y = 0) #+
  #facet_wrap(~Capacity,ncol = 2, scales = "fixed")
ggplotly(p)
```

The purple colors seem low, which indicates high capacity has low quantity.

```{r By RPM}
#length(unique(CFG.info$RPM))

# Extract Quarterly Sales for each CFG
data.joined %>% 
  group_by(CFG,Fiscal_Qtr,RPM) %>%
  summarise(HDD_QTY=sum(PART_QTY)) -> temp_qtr

temp_qtr$RPM <- as.factor(temp_qtr$RPM)

p <- temp_qtr %>% ggplot(aes(x=Fiscal_Qtr,y=HDD_QTY,group = CFG, color = RPM)) +
  geom_point(size = 2) +
  geom_line(size = 1.5,alpha=0.6) +
  labs(title = 'HDD Quarterly Sales by RPM', x = "Fiscal Quarter", y = "Part Quantity") +
  theme_minimal(base_size = 14) +
  scale_color_tableau('tableau10medium') +
  scale_x_discrete(breaks = c('FY17Q1', 'FY18Q1', 'FY19Q1')) +
  scale_y_continuous(label=comma) + expand_limits(y = 0) +
  facet_wrap(~RPM,ncol = 2, scales = "fixed")
ggplotly(p)
```
Two CFGs belong to 5900 and the quantity is very low and even none in FY19Q1.
7200 CFGs overall seem very stable.
10000 CFGs have large variety in the quantity as well as in the trend.
15000 CFGs show two subgroups: one is decreasing and the other group is relatively stable.


```{r By Interface_All}
#length(unique(CFG.info$Interface_All))

# Extract Quarterly Sales for each CFG
data.joined %>% 
  group_by(CFG,Fiscal_Qtr,Interface_All) %>%
  summarise(HDD_QTY=sum(PART_QTY)) -> temp_qtr

p <- temp_qtr %>% ggplot(aes(x=Fiscal_Qtr,y=HDD_QTY,group = CFG, color = Interface_All)) +
  geom_point(size = 2) +
  geom_line(size = 1.5,alpha=0.6) +
  labs(title = 'HDD Quarterly Sales by Interface All', x = "Fiscal Quarter", y = "Part Quantity") +
  theme_minimal(base_size = 14) +
  scale_color_tableau('tableau10medium') +
  scale_x_discrete(breaks = c('FY17Q1', 'FY18Q1', 'FY19Q1')) +
  scale_y_continuous(label=comma) + expand_limits(y = 0) +
  facet_wrap(~Interface_All,ncol = 2, scales = "fixed")
ggplotly(p)
```
There are only two CFGs that belong to SATA3G and the quantity became very loww in FY19Q1.
SAS6G CFGs are also very low in the past year FY18.
Almost all SATA6G CFGs are below 100,000 and their trends are stable.
Some of the SAS12G CFGs have higher quantity than 100,000.


```{r By Form_Factor}
#length(unique(CFG.info$Form_Factor))

# Extract Quarterly Sales for each CFG
data.joined %>% 
  group_by(CFG,Fiscal_Qtr,Form_Factor) %>%
  summarise(HDD_QTY=sum(PART_QTY)) -> temp_qtr

temp_qtr$Form_Factor <- as.factor(temp_qtr$Form_Factor)

p <- temp_qtr %>% ggplot(aes(x=Fiscal_Qtr,y=HDD_QTY,group = CFG, color = Form_Factor)) +
  geom_point(size = 2) +
  geom_line(size = 1.5,alpha=0.6) +
  labs(title = 'HDD Quarterly Sales by Form Factor', x = "Fiscal Quarter", y = "Part Quantity") +
  theme_minimal(base_size = 14) +
  scale_color_tableau('tableau10medium') +
  scale_x_discrete(breaks = c('FY17Q1', 'FY18Q1', 'FY19Q1')) +
  scale_y_continuous(label=comma) + expand_limits(y = 0) +
  facet_wrap(~Form_Factor,ncol = 2, scales = "fixed")
ggplotly(p)
```

It seems that there are more abnormal high trends in 2.5, which inspires me to do abnormal detection and then cluster CFGs.I do not think Form Factors affect the trend a lot since I do not see obvious difference between 2.5 and 3.5.